### 2025-01-05 manuscript.tex
Continued explaining reinforcement learning.

			\subsubsection{Reinforcement learning}
			In reinforcement learning, a virtual object called an agent can make observation of its environment, commit actions resulting in rewards or penalties (usually defined as negative rewards) based on the outcome. \cite{HMLSKT}\\ 
			In reinforcement learning, the goal is to figure out a strategy (called a policy) that tells the agent what actions to take in different situations, in order to get the most reward over time. The policy can either be deterministic, where the the agent always picks the same action for a given situation, or stochastic, where the action is chosen based on chance, according to a probability distribution. The agent needs to learn how actions and rewards are connected, which means it needs to explore the policy space. Policy space refers to the set of all possible policies that an agent can adopt. \cite{RLRAS}\\
			More precisely, this policy could be a neural network, which takes observations as inputs and outputs the resulting action. Alternatively, the policy could be a genetic algorithm, where each generation consists of multiple policies and new generations of policy offsprings are created based on the genetic algorithm used. Reinforcement learning is commonly used in robotics and smart home appliances like thermostats. We can also find financial securities trading support systems using reinforcement learning. \cite{HMLSKT}\\
			https://neptune.ai/blog/7-applications-of-reinforcement-learning-in-finance-and-trading\\
			https://github.com/pskrunner14/trading-bot\\
			https://github.com/selimamrouni/Deep-Portfolio-Management-Reinforcement-Learning\\
			https://github.com/doncat99/StockRecommendSystem\\ 
			\textbf{Algorithms}\\
			CONTINUE: EXPLAIN COMMON ALGORITHMS MORE IN DEPTH\\

>>>>

			\subsubsection{Reinforcement learning}
			In reinforcement learning, a virtual object called an agent can make observation of its environment, commit actions resulting in rewards or penalties (usually defined as negative rewards) based on the outcome. \cite{HMLSKT}\\ 
			In reinforcement learning, the goal is to figure out a strategy (called a policy) that tells the agent what actions to take in different situations, in order to get the most reward over time. The policy can either be deterministic, where the the agent always picks the same action for a given situation, or stochastic, where the action is chosen probabilistically. The agent needs to learn how actions and rewards are connected, which means it needs to explore the policy space through trial and error. Policy space refers to the set of all possible policies that an agent can adopt. \cite{RLRAS}\\
			More precisely, this policy could be a neural network, which takes observations as inputs and outputs the resulting action. Alternatively, the policy could be a genetic algorithm, where each generation consists of multiple policies and new generations of policy offsprings are created based on the genetic algorithm used. Reinforcement learning is commonly used in robotics and smart home appliances like thermostats. We can also find financial securities trading support systems using reinforcement learning. \cite{HMLSKT}\\
			A good example of a common approach in algorithmic trading can be illustrated by the "Stock Trading Bot using Deep Q-Learning" project created by Prabhsimran Singh. This project demonstrates an automatic stock trading bot using Deep Q-Learning, a type of reinforcement learning algorithm utilizing a deep neural network to approximate the optimal action-value function (also known as Q-function), which determines the best action to take in a given state. \cite{HCTDRL}. At any moment, the agent observes its current state (an n-day window of stock prices, which shows the stock prices of the last n days), selects and performs a buy/hold/sell action. The next state is evaluated and the agent receives a reward accordingly, based on changes in the portfolio value. The agent then updates its parameters by minimizing the computed loss, which refers to the differnece between the target Q-value and the predicted Q-value, with the Q-value defining the optimal state-action (quality) values \cite{HMLSKT}. \cite{STBDQ}\\
			https://neptune.ai/blog/7-applications-of-reinforcement-learning-in-finance-and-trading\\
			https://github.com/selimamrouni/Deep-Portfolio-Management-Reinforcement-Learning\\
			https://github.com/doncat99/StockRecommendSystem\\ 
			\textbf{Algorithms}\\
			CONTINUE: EXPLAIN COMMON ALGORITHMS MORE IN DEPTH\\
